Determinism, Complexity, and Predictability in Computer Performance

### 2014-04-11 model.tex
filled in the stuff about geometry of p vs c

  \begin{subfigure}{0.6\columnwidth}
    \includegraphics[width=\columnwidth]{figs/colRWForecast.png}
    \caption{\col\\ random walk }
    \label{fig:gccMEAN}
  \end{subfigure}%
   \begin{subfigure}{0.6\columnwidth}
    \includegraphics[width=\columnwidth]{figs/gccRWForecast.png}
    \caption{\gcc\\ random walk }
    \label{fig:gccMEAN}
  \end{subfigure}% 
     \begin{subfigure}{0.6\columnwidth}
    \includegraphics[width=\columnwidth]{figs/svdfiveRWForecast.png}
    \caption{\svdfive\\ random walk}
    \label{fig:gccMEAN}
  \end{subfigure}%      
  \\  
      \begin{subfigure}{0.6\columnwidth}
    \includegraphics[width=\columnwidth]{figs/colMeanForecast.png}
    \caption{\col\\ na\"ive }
    \label{fig:gccMEAN}
  \end{subfigure}%
   \begin{subfigure}{0.6\columnwidth}
    \includegraphics[width=\columnwidth]{figs/gccMeanForecast.png}
    \caption{\gcc\\ na\"ive }
    \label{fig:gccMEAN}
  \end{subfigure}% 
     \begin{subfigure}{0.6\columnwidth}
    \includegraphics[width=\columnwidth]{figs/svdfiveMeanForecast.png}
    \caption{\svdfive\\ na\"ive }
    \label{fig:gccMEAN}
  \end{subfigure}%      
  \\
    \begin{subfigure}{0.6\columnwidth}
    \includegraphics[width=\columnwidth]{figs/colARIMAForecast.png}

    \caption{\col \\ ARIMA}
    \label{fig:colARIMA}
  \end{subfigure}
  \begin{subfigure}{0.6\columnwidth}
    \includegraphics[width=\columnwidth]{figs/gccARIMAForecast.png}
    \caption{\gcc \\ ARIMA }
    \label{fig:gccARIMA}
  \end{subfigure}%
  \begin{subfigure}{0.6\columnwidth}
    \includegraphics[width=\columnwidth]{figs/svdfiveARIMAForecast.png}
    \caption{\svdfive \\ ARIMA }
    \label{fig:gccARIMA}
  \end{subfigure}%    
  \\

      \begin{subfigure}{0.6\columnwidth}
    \includegraphics[width=\columnwidth]{figs/colLMAForecast.png}
    \caption{\col \\ LMA}
    \label{fig:colLMA}
  \end{subfigure}
      \begin{subfigure}{0.6\columnwidth}
    \includegraphics[width=\columnwidth]{figs/gccLMAForecast.png}
    \caption{\gcc \\ LMA}
    \label{fig:gccLMA}
  \end{subfigure}  
        \begin{subfigure}{0.6\columnwidth}
    \includegraphics[width=\columnwidth]{figs/svdfiveLMAForecast.png}
    \caption{\svdfive \\ LMA}
    \label{fig:gccLMA}
  \end{subfigure}
  %\begin{subfigure}{0.5\textwidth}
  %  \includegraphics[width=1.0\textwidth]{figs/LMA_vs_ARIMA}
   \caption{Predicted ($p_j$) versus true values ($c_j$) for
     forecasts of \col, \gcc, and \svdfive.  On this type of plot, a
     perfect prediction lies exactly on the diagonal.
%
%
}
\label{fig:forecast-example}
  %\end{subfigure}
\end{figure*} 
In these images, the vertical axis is the prediction $p_j$ and the
horizontal axis is the true continuation $c_j$.  On such a plot, a
perfect prediction would lie on the diagonal.  LMA, for instance,
generates a very accurate prediction of the \col data, while ARIMA
does not.  Horizontal lines result when a constant predictor (e.g.,
\naive) is used on a non-constant signal.  Point clouds reflect the
structure of the distribution of the errors---roughly normally
distributed, for example, in the case of LMA on \gcc. The triangular 
shapes that ARIMA and random-walk produce for \col simply reflects 
three phases of values that is visually present in the time-series.{\color{red}not happy with this explanation, I(joshua) will think about how to word this}

>>>>

  \begin{subfigure}{0.6\columnwidth}
    \includegraphics[width=\columnwidth]{figs/colRWForecast.png}
    \caption{\col\\ random walk }
    \label{fig:colRW}
  \end{subfigure}%
   \begin{subfigure}{0.6\columnwidth}
    \includegraphics[width=\columnwidth]{figs/gccRWForecast.png}
    \caption{\gcc\\ random walk }
    \label{fig:gccRW}
  \end{subfigure}% 
     \begin{subfigure}{0.6\columnwidth}
    \includegraphics[width=\columnwidth]{figs/svdfiveRWForecast.png}
    \caption{\svdfive\\ random walk}
    \label{fig:svd5RW}
  \end{subfigure}%      
  \\  
      \begin{subfigure}{0.6\columnwidth}
    \includegraphics[width=\columnwidth]{figs/colMeanForecast.png}
    \caption{\col\\ na\"ive }
    \label{fig:colMEAN}
  \end{subfigure}%
   \begin{subfigure}{0.6\columnwidth}
    \includegraphics[width=\columnwidth]{figs/gccMeanForecast.png}
    \caption{\gcc\\ na\"ive }
    \label{fig:gccMEAN}
  \end{subfigure}% 
     \begin{subfigure}{0.6\columnwidth}
    \includegraphics[width=\columnwidth]{figs/svdfiveMeanForecast.png}
    \caption{\svdfive\\ na\"ive }
    \label{fig:svd5MEAN}
  \end{subfigure}%      
  \\
    \begin{subfigure}{0.6\columnwidth}
    \includegraphics[width=\columnwidth]{figs/colARIMAForecast.png}
    \caption{\col \\ ARIMA}
    \label{fig:colARIMA}
  \end{subfigure}
  \begin{subfigure}{0.6\columnwidth}
    \includegraphics[width=\columnwidth]{figs/gccARIMAForecast.png}
    \caption{\gcc \\ ARIMA }
    \label{fig:gccARIMA}
  \end{subfigure}%
  \begin{subfigure}{0.6\columnwidth}
    \includegraphics[width=\columnwidth]{figs/svdfiveARIMAForecast.png}
    \caption{\svdfive \\ ARIMA }
    \label{fig:svd5ARIMA}
  \end{subfigure}%    
  \\

      \begin{subfigure}{0.6\columnwidth}
    \includegraphics[width=\columnwidth]{figs/colLMAForecast.png}
    \caption{\col \\ LMA}
    \label{fig:colLMA}
  \end{subfigure}
      \begin{subfigure}{0.6\columnwidth}
    \includegraphics[width=\columnwidth]{figs/gccLMAForecast.png}
    \caption{\gcc \\ LMA}
    \label{fig:gccLMA}
  \end{subfigure}  
        \begin{subfigure}{0.6\columnwidth}
    \includegraphics[width=\columnwidth]{figs/svdfiveLMAForecast.png}
    \caption{\svdfive \\ LMA}
    \label{fig:gccLMA}
  \end{subfigure}
  %\begin{subfigure}{0.5\textwidth}
  %  \includegraphics[width=1.0\textwidth]{figs/LMA_vs_ARIMA}
   \caption{Predicted ($p_j$) versus true values ($c_j$) for
     forecasts of \col, \gcc, and \svdfive.  On this type of plot, a
     perfect prediction lies exactly on the diagonal.
%
%
}
\label{fig:forecast-example}
  %\end{subfigure}
\end{figure*} 
In these images, the vertical axis is the prediction $p_j$ and the
horizontal axis is the true continuation $c_j$.  On such a plot, a
perfect prediction would lie on the diagonal.  LMA, for instance,
generates a very accurate prediction of the \col data, while ARIMA
does not.  Horizontal lines result when a constant predictor (e.g.,
\naive) is used on a non-constant signal.  Point clouds reflect the
structure of the distribution of the errors---roughly normally
distributed, for example, in the case of LMA on \gcc.  The shapes of
Figures~\ref{fig:colRW} and~\ref{fig:colARIMA} are reminiscent of the
projected embedding in Figure~\ref{fig:embedding}(a).  For a
random-walk predictor, a $p_j$ vs. $c_j$ plot is equivalent to a
two-dimensional embedding with $\tau=1$.  For ARIMA, the
correspondence is not quite as simple, since the $p_j$ values are
linear combinations of a number of past values of the $c_j$, but the
effect is largely the same\footnote{The temporal ordering of the
  points on the ARIMA $p_j$ vs. $c_j$ plot does not match that of a
  projected embedding of the time series, however.}.
